---
title: "In-class Activity - Week 2"
author: "Tengyu Song"
date: "2025-01-29"
toc: true
number-sections: false
highlight-style: pygments
format: 
  html: 
    code-fold: false
    html-math-method: katex
theme:
  - cosmo
---

# Advanced use of R
## Lists are your friends

**Create a list pointing to (i) the integer vector 1:5, (ii) the numeric vector 1:5 / 5, and (iii) the character vector letters[1:5]. Call this object a, and the individual elements i, ii, iii.**

```{r}
a <- list(i = 1:5, ii = 1:5 / 5, iii = letters[1:5])
a
```


**(a) Write a simple function which takes such a list of the form of a and a power argument, and raises the numbers in element ii to the given power. Call the function on the list you created and assign the return value to a new name, e.g., b. Print the addresses of the objects in the original list and the modified list with the function lobstr::ref().**

```{r}
library(lobstr)
power <- function(x, p) {
  x$ii <- x$ii ^ p
  return(x)
}
b <- power(a, 2)
cat("Address of a:\n")
ref(a)
cat("Address of b:\n")
ref(b)
```

Notice that the address to the second element of list a is different from the address to the second element of list b, while the other two elements are the same. This is because the second element of list a is modified by the function.


**(b)Combine several of these lists into a new list, I’ll call it c. Now extract the elements i from the lists in c with lapply(), using the access operator [[, and assign it to a new name. Inspect the references in this new object with lobstr::ref(). **

```{r}
a1 <- list(i = 1:5, ii = 1:5 / 5, iii = letters[1:5])
a2 <- list(i = 1:5, ii = 1:5 / 5, iii = letters[1:5])

c <- list(a1, a2)
e1 <- lapply(c, function(x) x[[1]])

cat("Address of elements in a1:\n")
ref(a1)
cat("Address of elements in a2:\n")
ref(a2)
cat("Address of elements in e1:\n")
ref(e1)
```

The addresses of the extracted elements align with the addresses of the original elements in a1 and a2.


**(c) Do the same as in b, but now use sapply() instead. Is it the same as in b or are there differences? What do we learn from that?**

```{r}
e2 <- sapply(c, function(x) x[[1]])
cat("Address of elements in e2:\n")
ref(e2)
```

The result from `sapply()` is different from `lapply()`. Instead of a list, `e2` is a vector and `ref` returns a single address.

## Vector layout and subsetting

**Create atomic vector of length 1,000,000. Coerce this vector into a matrix of dimensions 2000 by 500 using (a) the matrix() function and (b) the dim attribute. Which one would you prefer and why?**

```{r}
x <- 1:1000000
m1 <- matrix(x, nrow = 2000)
m2 <- x
dim(m2) <- c(2000, 500)
# show the dimension of the two matrices
dim(m1)
dim(m2)
```

The two methods yield the same result. I prefer the first one because it is more explicit and easier to read.

**(a) Of the matrix you created before select the 50th element of the 11th column using the matrix index and the flat index.**

```{r}
# matrix index
cat(m1[50, 11], "\n")
# flat index
cat(m1[50 + 11 * 2000], "\n")
```

**(b) Now select the 36,321-th element using the flat index and the matrix index.**

```{r}
# flat index
cat(m1[36321], "\n")
# matrix index
cat(m1[36321 %% 2000, 36321 %/% 2000 + 1], "\n")
```

## Batch Processing

**Create a new R script that accepts the following arguments:**

**number of replications (integer > 0), output directory and which simply prints the values of these arguments to the console.**

**Run this R script from within your project directory.**

The answer for this question is in the file `batch_processing.R`.


# Basics of python

**Create a new python script and add the following lines to it:
**

```python
def main():
  ...

if __name__ == "__main__":
  main()
```
**Add a comment to briefly explain what this boilerplate code is doing.**

The answer for this question is in the file `python_code.py`.